ANGSD-wrapper: utilities for analyzing next generation sequencing data

### 2016-05-30 manuscript.tex
fixed manuscript

High throughput sequencing has revolutionized evolutionary genetics, allowing researchers to quickly assay large numbers of individuals and examine genome-wide variation. 
Application of these approaches has led to changes in both experimental design and data analysis \citep{ekblom2011applications}. 
Many popular software packages used by researchers for analysis of comparative resequencing data \citep[see][]{excoffier2006computer} were not designed to handle these novel data types or efficiently analyze the large volumes of data now being generated. 
Despite the decreasing cost of sequencing, researchers must nonetheless allocate finite resources and balance the depth of sequencing and the breadth of a sample. 
This poses a challenge for population genetics analysis, which generally requires accurate polymorphism calls in a broad sample \citep{pluzhnikov1996optimal, felsenstein2006accuracy}. 
While these experimental design challenges in molecular population genetic studies have existed for at least two decades, high throughput sequencing brings the added technical challenges of highly variable coverage, missing data, and high per-nucleotide error rates \citep{}.

>>>>

High throughput sequencing has revolutionized evolutionary genetics, allowing researchers to quickly assay large numbers of individuals and examine genome-wide variation. 
Application of these approaches has led to changes in both experimental design and data analysis \citep{ekblom2011applications}. 
Many popular software packages used by researchers for analysis of comparative resequencing data \citep[see][]{excoffier2006computer} were not designed to handle these novel data types or efficiently analyze the large volumes of data now being generated. 
Despite the decreasing cost of sequencing, researchers must nonetheless allocate finite resources and balance the depth of sequencing and the breadth of a sample. 
This poses a challenge for population genetics analysis, which generally requires accurate polymorphism calls in a broad sample \citep{pluzhnikov1996optimal, felsenstein2006accuracy}. 
While these experimental design challenges in molecular population genetic studies have existed for at least two decades, high throughput sequencing brings the added technical challenges of highly variable coverage, missing data, and high per-nucleotide error rates \citep{lynch2008diversity, johnson2007bias}.
